\chapter*{参考文献}
{\zihao{6}
Abraham, R. \& Marsden, J. E. (1978) \textit{Foundations of Mechanics}, 2nd edn (Benjamin/Cummings, Reading, Mass.).

Adler, R., Bazin, M., \& Schiffer, M. (1975) \textit{Introduction to General Relativity}, 2nd edn
(McGraw-Hill, New York).

Alcubierre, M. (2008) \textit{Introduction to 3+1 Numerical Relativity} (Oxford University Press,
Oxford).

Allen, S. W., Schmidt, R. W., \& Fabian, A. C. (2002) Mon. Not. Roy. Astron. Soc., 334, L11.

Andersson, N., Kokkotas, K.D., \& Schutz, B.F. (1999) Astrophys. J., 510, 846–853.

Andréasson, H. (2005) ‘The Einstein–Vlasov system/kinetic 
theory’, Living Rev. Relativity, 8, 2. URL: \url{http://www.livingreviews.org/lrr-2005-2}

Ansorg, M. (2005) Phys. Rev., D72, 024019.

Armstrong, J. W. (2006) ‘Low-frequency gravitational wave searches using spacecraft doppler Tracking’, Living Rev. Relativity, 9, 1. URL: \url{http://www.livingreviews.org/lrr-2006-1}


Arzeliès, H. (1966) Relativistic Kinematics (Pergamon Press, London). Translation of a 1955 French edn.


Ashby, N. (2003) ‘Relativity in the global positioning system’, Living Rev. Relativity, 6, 1.
URL: \url{http://www.livingreviews.org/lrr-2003-1}


Ashtekar, A. \& Bojowald, M. (2006) Class. Q. Grav., 23, 391.


Balian, R., Audouze, J., \& Schramm, D. N. (1980) Physical Cosmology. Proceedings of 1979 Les Houches summer school (North-Holland, Amsterdam).


Barrow, J. \& Tipler, F. (1986) The Anthropic Cosmological Principle (Oxford University Press, Oxford).


Bekenstein, J. D. (1973) Phys. Rev. D, 7, 2333–2346.


Bekenstein, J. D. (1974) Phys. Rev. D, 9, 3292–3300.


Berger, B. K. (2002) ‘Numerical approaches to spacetime singularities’, Living Rev. Relativity, 5, 1. URL: \url{http://www.livingreviews.org/lrr-2002-1}


Beyer, H. R. (2001) Comm. Math. Phys., 221, 659–676.


Birrell, N. D. \& Davies, P. C. W. (1984) Quantum Fields in Curved Space (Cambridge University Press, Cambridge).


Bishop, R. L. \& Goldberg, S. I. (1981) Tensor Analysis on Manifolds (Dover, New York).


Blair, D. (1991) The Detection of Gravitational Waves (Cambridge).


Blanchet, L. (2006) ‘Gravitational radiation from post-Newtonian sources and inspiralling compact binaries’, Living Rev. Relativity, 9, 4. URL: \url{http://www.livingreviews.org/lrr-2006-4}

Blandford, R. D. \& Znajek, R. L. (1977) Mon. Not. Roy. astr. Soc., 179 433–456.


Bohm, D. (2008) The Special Theory of Relativity, new edition with preface by J. Barrow (Routledge, New York).


Bojowald, M. (2005) ‘Loop quantum cosmology’, Living Rev. Relativity, 8, 11. URL: \url{http://www.livingreviews.org/lrr-2005-11}


Bona, C. \& Palenzuela-Luque, C. (2005) Elements of Numerical Relativity (Springer, Berlin).


Boriakoff, V., Ferguson, D. C., Haugan, M. P., Terzian, Y., \& Teukolsky, S. A. (1982) Astrophys. J., 261, L101.


Bourne, D. E. \& Kendall, P. C. (1992) Vector Analysis and Cartesian Tensors 3rd edn  (CRC Press, New York).


Brenneman, L. \& Reynolds, C. (2006) Astrophys. J., 652 1028. 

Buchdahl, H. A. (1959) Phys. Rev., 116, 1027.


Buchdahl, H. A. (1981) Seventeen Simple Lectures on General Relativity Theory (Wiley, New York).


Butterworth, E. M. \& Ipser, J. R. (1976) Astrophys. J., 204, 200. 

Campanelli, M., Lousto, C. O., Zlochower, Y., \& Merritt, D. (2007) Phys. Rev. Lett., 98, 231102.


Carroll, S. (2003) Spacetime and Geometry (Benjamin Cummings).


Cartan, E. (1923) Ann. Ecole Norm. Sup., 40, 325.


Carter, B. (1969) J. Math. Phys., 10, 70.


Carter, B. (1973) In DeWitt, B. \& De Witt, C. (eds.). Black Holes (Gordon and Breach, New York).


Carter, B. (1979) ‘The general theory of the mechanical, electromagnetic, and thermodynamic properties of black holes’. In Hawking \& Israel (1979), p. 294.


Caves, C. M., Thorne, K. S., Drever, R. W. P., Sandberg, V. D., \& Zimmerman, M. (1980) Rev. Mod. Phys., 52, 341.


Chandrasekhar, S. (1957) Stellar Structure (Dover, New York).


Chandrasekhar, S. (1980) In Wayman, P., Highlights of Astronomy (Reidel, Dordrecht).Proceedings of the 1979 IAU meeting in Montreal, p. 45.


Chandrasekhar, S. (1983) The Mathematical Theory of Black Holes (Oxford University Press).


Chandrasekhar, S. (1987) Truth and Beauty (University of Chicago Press, Chicago).


Choquet-Bruhat, Y., DeWitt-Morette, C., \& Dillard-Bleick, M. (1977) Analysis, Manifolds, and Physics (North-Holland, Amsterdam).


Choquet-Bruhat, Y. \& York, J. W. (1980) ‘The Cauchy problem’. In Held (1980a), p. 99.


Ciufolini, I., Pavlis, E. C., \& Peron, R. (2006) New Astronomy, 11, 527–550.


Comins, N. \& Schutz, B. F. (1978) Proc. Roy. Soc. A, 364, 211.


Cook, G. (2000) ‘Initial Data for Numerical Relativity’, Living Rev. Relativity, 3, 5. URL:
\url{http://www.livingreviews.org/lrr-2000-5}



Cordes, J. M., Kramer, M., Lazio, T. J. W., et al. (2004) New Astr. Rev., 48, 1413–1438.


Damour, T. (1987) ‘The problem of motion in Newtonian and Einsteinian gravity’, in S.


Hawking and W. Israel (eds.), 300 Years of Gravitation (Cambridge), 128–198.
Damour, T. \& Dervelle, N. (1986) Ann. Inst. Henri Poincare 44, 263–292.


DeWitt, B. S. (1979) ‘Quantum gravity: the new synthesis’. In Hawking \& Israel (1979), p. 680.


Dicke, R. H. (1964) In Dewitt, B. \& Dewitt, C. Relativity, Groups and Topology (Gordon and Breach, New York). Lectures at the 1963 Les Houches summer school.


Dixon, W. G. (1978) Special Relativity: The Foundation of Macroscopic Physics (Cambridge University Press, Cambridge).


Ehlers, J., and Kundt, W. (1962), in Witten, L., ed., Gravitation: An Introduction to Current Research (Wiley, New York), pp. 49–101.


Fermi, E. (1956) Thermodynamics (Dover, New York).
Filippenko, A. (2008) Dark Energy and Supernovae (Princeton University Press, Princeton).


French, A. P. (1968) Special Relativity (W. W. Norton, New York).


Friedman, J. L. (1978) Commun. Math. Phys., 63, 243.


Friedman, J. L. \& Schutz, B. F. (1978) Astrophys. J., 222, 281.


Futamase, T. (1983) Phys. Rev. D, 28, 2373.


Futamase, T. \& Itoh, Y. (2007), Living Rev. Relativity, 10, 2. URL: \url{http://www.livingreviews.org/lrr-2007-2}


Futamase, T. \& Schutz, B. F. (1983) Phys. Rev. D, 28, 2363.


Genzel, R. \& Karas, V. (2007) in V. Karas and G. Matt (eds.) Black Holes (Cambridge University Press, Cambridge), pp. 173–180.


Geroch, R. (1978) General Relativity from A to B (University of Chicago Press).


Geroch, R. \& Horowitz, G. T. (1979) ‘Global structure of spacetimes’. In Hawking \& Israel (1979), p. 212.


Glendenning, N. K. (2007) Special and General Relativity: With Applications to White Dwarfs, Neutron Stars and Black Holes (Springer, New York).


Gron, O. \& Hervik, S. (2007) Einstein’s General Theory of Relativity: With Modern Applications in Cosmology (Springer, New York).


Guth, A. (1981) Phys. Rev. D, 23, 347.


Hagedorn, R. (1963) Relativistic Kinematics (Benjamin, New York).


Hansen, C. J., Kawaler, S. D., \& Trimble, V. (2004) Stellar Interiors – Physical Principles, Structure, and Evolution (Springer-Verlag, New York).


Harrison, B. K., Thorne, K. S., Wakano, M., \& Wheeler, J. A. (1965) Gravitation Theory and Gravitational Collapse (University of Chicago Press).


Hartle, J. B. (2003) Gravity: An Introduction to Einstein’s General Relativity (Benjamin Cummings).


Hawking, S. W. (1972) Commun. Math. Phys., 25, 152.


Hawking, S. W. (1975) Commun. Math. Phys., 43, 199.


Hawking, S. W. \& Ellis, G. F. R. (1973) The Large-Scale Structure of Space–Time (Cambridge University Press, Cambridge).


Hawking, S. W. \& Israel, W. (1979) General Relativity: An Einstein Centenary Survey (Cambridge University Press, Cambridge).


Heidmann, J. (1980) Relativistic Cosmology (Springer, Berlin).


Held, A. (1980a) General Relativity and Gravitation (Plenum, London), vol. 1.


Held, A. (1980b) General Relativity and Gravitation (Plenum, London), vol. 2.


Hermann, R. (1968) Differential Geometry and the Calculus of Variations (Academic Press, New York).


Hicks, N. J. (1965) Notes on Differential Geometry (D. Van Nostrand, New York).


Heusler,M.(1998)‘Stationaryblackholes:uniquenessandbeyond’, LivingRev.Relativity, 1, 6. URL: \url{http://www.livingreviews.org/lrr-1998-6}


Hobson, M. P., Efstathiou, G. P., \& Lasenby, A. N. (2006) General Relativity: An Introduction for Physicists (Cambridge University Press, Cambridge).


Hoffmann, B. (1983) Relativity and Its Roots (Dover, New York).


Höflich, P., Kumar, P., \& Wheeler, J. C. (2004) Cosmic Explosions in Three Dimensions: Asymmetries in Supernovae and Gamma-Ray Bursts (Cambridge University Press,
Cambridge).


Hough, J. L. and Rowan, S. (2000) ‘Gravitational wave detection by interferometry (ground and space)’, Living Rev. Relativity, 3, 3. URL: \url{http://www.livingreviews.org/lrr-2000-3}


Hulse, R. A. and Taylor, J. H. (1975) ‘Discovery of a pulsar in a binary system’, Astrophys. J., 195, L51–L53.


Isham, C. J. (1999) Modern Differential Geometry for Physicists (World Scientific, Singapore).


Israel, W. \& Stewart, J. (1980) ‘Progress in relativistic thermodynamics and electrodynamics of continuous media’. In Held (1980), p. 491.


Jackson, J. D. (1975) Classical Electrodynamics (Wiley, New York).


Kilmister, C. W. (1970) Special Theory of Relativity (Pergamon, Oxford).


Knop, R.A. et al. (2003) Astrophys. J., 598, 102.


Kobayashi, S. \& Nomizu, K. (1963) Foundations of 

Differential Geometry (Interscience, New York), vol. I.


Kobayashi, S. \& Nomizu, K. (1969) Foundations of Differential Geometry (Interscience, New York), vol II.


Kokkotas, K. D. \& Schmidt, B. (1999) ‘Quasi-normal modes of stars and black holes’, Living Rev. Relativity, 2, 2. URL: \url{http://www.livingreviews.org/lrr-1999-2}


Komossa, S., Zhou, H., \& Lu, H. (2008) ‘A recoiling supermassive black hole in the quasar SDSS J092712.65+294344.0?’, Astrophys. J. Lett., 678, L81–L84.


Kramer, M. et al. (2006) Science, 314, 97–102.


Landau, L. D. \& Lifshitz, E. M. (1959) Fluid Mechanics (Pergamon, Oxford).


Landau,L.D.\&Lifshitz,E.M.(1962)TheClassicalTheoryofFields(Pergamon,Oxford).


Lattimer, J. M. \& Prakash, M. (2000) ‘Nuclear matter and its role in supernovae, neutron stars and compact object binary mergers’, Phys. Rep., 333 121–146.


Liang, E. P. T. \& Sachs, R. K. (1980) ‘Cosmology’. In Held (1980b), p. 329.


Liddle, A. (2003) An Introduction to Modern Cosmology, 2nd. edn (Wiley, New York).


Lightman, A. P., Press, W. H., Price, R. H., \& Teukolsky, S. A. (1975) Problem Book inRelativity and Gravitation (Princeton University Press, Princeton).


Linde, A. (1982) Phys. Lett., 108B, 389.


Lorimer, D. R. (2008) ‘Binary and millisecond pulsars’, Living Rev. Relativity, 11, 8. URL: \url{http://www.livingreviews.org/lrr-2008-8}


Lorimer, D. R. \& Kramer, M. (2004) Handbook of Pulsar Astronomy (Cambridge University Press, Cambridge).


Lovelock, D. \& Rund, H. (1990) Tensors, Differential Forms, and Variational Principles (Dover, New York).


Lyne, A.G. \& Smith, F. G. (1998) Pulsar Astronomy (Cambridge University Press, Cambridge).


Maartens, R. (2004) ‘Brane–world gravity’, Living Rev. Relativity, 7, 7. URL: \url{http://www. livingreviews.org/lrr-2004-7}


MacCallum, M. A. H. (1979) ‘Anisotropic and inhomogeneous relativistic cosmologies’. In Hawking \& Israel (1979), p. 533.


Mathews, J. \& Walker, R. L. (1965) Mathematical Methods of Physics (Benjamin, New York).


McCrea, W. H. (1979), Q. J. Roy. Astron. Soc., 20, 251.


Marder, L. (1971) Time and the Space-Traveller (George Allen \& Unwin, London).


Mermin, N. D. (1989) Space and Time in Special Relativity (Waveland Press, Illinois).


Merritt, D. and Milosavljevic, M. (2005) ‘Massive black hole binary evolution’, Living Rev. Relativity, 8, 8. URL: \url{http://www.livingreviews.org/lrr-2005-8}


Miller, M. C. \& Colbert, E. J. M. (2004) Int. J. Mod. Phys., D13, 1–64.


Misner, C. W., Thorne, K. S., \& Wheeler, J. A. (1973) Gravitation (Freeman, San Francisco).


Møller, C. (1972) The Theory of Relativity (Clarendon Press, Oxford).


Mukhanov, V. (2005) Physical Foundations of Cosmology (Cambridge University Press, Cambridge).


Pais, A. (1982) ‘Subtle is the Lord...’, The Science and the Life of Albert Einstein (Oxford University Press, Oxford).


Peebles, P. J. E. (1980) Large Scale Structure of the Universe (Princeton University Press).


Penrose, R. (1969), Rev. Nuovo Cimento 1, 252.


Penrose, R. (1979) In Hawking \& Israel (1979), 581.


Penzias, A. A. (1979) Rev. Mod. Phys., 51, 425.


Perlick, V. (2004) ‘Gravitational lensing from a spacetime perspective’, Living Rev. Relativity, 7, 9. URL: \url{http://www.livingreviews.org/lrr-2004-9}


Perlmutter, S., Aldering, G., Goldhaber, G., Knop, R.A., Nugent, P., Castro, P.G., Deustua, S., Fabbro, S., Goobar, A., Groom, D., Hook, I.M., Kim, A.G., Kim, M.Y., Lee, J.C.,
Nunes, N.J., Pain, R., Pennypacker, C.R., Quimby, R., Lidman, C., Ellis, R.S., Irwin, M., McMahon, R.G., Ruiz-Lapuente, P., Walton, N., Schaefer, B., Boyle, B.J., Filippenko, A.V., Matheson, T., Fruchter, A.S., Panagia, N., Newberg, H.J.M., and Couch, W.J., (1999), Astrophys. J., 517, 565–586. 

Peters, P. C. (1964) Phys. Rev., B 136, 1224.


Pound, R. V. \& Rebka, G. A. (1960) Phys. Rev. Lett., 4, 337.


Pound, R. V. \& Snider, J. L. (1965) Phys. Rev., B 140, 788.


Price, R. H. (1972a) Phys. Rev. D, 5, 2419.


Price, R. H. (1972b) Phys. Rev. D, 5, 2439.


Rendall, A. D. (2005) ‘Theorems on existence and global dynamics for the Einstein equations’, Living Rev. Relativity, 8, 6. URL: \url{http://www.livingreviews.
org/lrr-2005-6}


Renn, J. ed. (2007) The Genesis of General Relativity: Sources and Interpretations (Springer, 4 vols).


Riess, A.G., Filippenko, A.V., Challis, P., Clocchiatti, A., Diercks, A., Garnavich, P.M.,


Gilliland, R.L., Hogan, C.J., Jha, S., Kirshner, R.P., Leibundgut, B., Phillips, M.M.,


Reiss, D., Schmidt, B.P., Schommer, R.A., Smith, R.C., Spyromilio, J., Stubbs, C., Suntzeff, N.B., and Tonry, J. (1998) Astron. J., 116, 1009–1038.


Rindler, W. (1991) Introduction to Special Relativity, 2nd edn. (Oxford University Press, Oxford).


Rindler, W. (2006) Relativity: Special, General, Cosmological, 2nd edn. (Oxford University Press, Oxford).


Robinson, D. C. (1975) Phys. Rev. Lett., 34, 905.


Rovelli, C. (2004) Quantum Gravity (Cambridge University Press, Cambridge).


Ryan, M. P. \& Shepley, L. C. (1975) Homogeneous Relativistic Cosmologies (Princeton University Press).


Saulson, P. (1994) Funamentals of Interferometric Gravitational Wave Detectors (World Scientific).


Schild, A. (1967) In Ehlers, J. (ed.), Relativity Theory and Astrophysics: I. Relativity and Cosmology (American Math. Soc., Providence, R.I.).


Schneider, P. (2006) Extragalactic Astronomy and Cosmology (Springer-Verlag, Berlin).


Schneider, P., Ehlers, J., Falco, E. (1992) Gravitational Lenses (Springer-Verlag, Berlin).


Schouten, J. A. (1990) Tensor Analysis for Physicists (Dover, New York).


Schrödinger, E. (1950) Space-Time Structure (Cambridge University Press, Cambridge).


Schutz, B. F. (1980a) Phys. Rev., D 22, 249.


Schutz, B. F. (1980b) Geometrical Methods of Mathematical Physics (Cambridge University Press, Cambridge).


Schutz, B. F. (1984) Am. J. Phys., 52, 412.


Schutz, B. F. (1986) Nature, 323, 310–311.


Schutz, B. F. (2003) Gravity from the Ground Up (Cambridge University Press, Cambridge).


Schutz, B. F. \& Ricci, F. (2001) in I. Ciufolini, et al. (eds.) Gravitational Waves (Inst. of Phys., Bristol), pp. 11–83.


Schwarz, P. M. \& Schwarz, J. H. (2004) Special Relativity: From Einstein to Strings (Cambridge University Press, Cambridge).


Shapiro, I. I. (1980) ‘Experimental tests of the general theory of relativity’. In Held (1980b), p. 469.


Shapiro, S. L. \& Teukolsky, S. A. (1983) Black Holes, White Dwarfs, and Neutron Stars (Wiley, New York).


Smarr, L. L. (ed.) (1979) Sources of Gravitational Radiation (Cambridge University Press, Cambridge).


Spergel, D. N. et al (2003) Astrophys. J. Suppl., 148 175.


Spivak, M. (1979) A Comprehensive Introduction to Differential Geometry, (Publish or Perish, Boston), vols. 1–5.


Stairs, I. H. (2003) ‘Testing general relativity with pulsar timing’, Living Rev. Relativity, 6,
5. URL: \url{http://www.livingreviews.org/lrr-2003-5}


Starobinsky, A. (1980) Phys. Lett., 91B, 99.


Stephani, H. (2004) Relativity: An Introduction to Special and General Relativity, 3rd edn (Cambridge University Press, Cambridge).


Stephani, H., Kramer, D., MacCallum, M., Hoenselaers, C., and Herlt, E. (2003), Exact Solutions of Einstein’s Field Equations, 2nd edn (Cambridge UniversityPress).


Stergioulas, N. (2003) ‘Rotating Stars in Relativity’, Living Rev. Relativity 6, 3. URL:
\url{http://www.livingreviews.org/lrr-2003-3}


Synge, J. L. (1960) Relativity: The General Theory (North-Holland, Amsterdam).


Synge, J. L. (1965) Relativity: The Special Theory (North-Holland, Amsterdam).


Tayler, R. J. (1994) The Stars: their Structure and Evolution, 2nd edn (Cambridge University Press, Cambridge).


Taylor, E. F. \& Wheeler, J. A. (1966) Spacetime Physics (Freeman, San Francisco).


Taylor, J. H. \& Weisberg, J. M. (1982) Astrophys. J., 253, 908.


Terletskii, Y. P. (1968) Paradoxes in the Theory of Relativity (Plenum, New York).


Teukolsky, S. A. (1972) Phys. Rev. Lett., 29, 114.


Thiemann, T. (2007) Modern Canonical Quantum General Relativity (Cambridge University Press, Cambridge).


Thorne, K. S., Caves, C. M., Sandberg, V. D., \& Zimmerman, M. (1979) ‘The quantum limit for gravitational-wave detectors and methods of circumventing it’. In Smarr
(1979a), p. 49.


Tipler, F. J., Clarke, C. J. S., \& Ellis, G. F. R. (1980), ‘Singularities and horizons – a review article’. In Held (1980b), p. 97.


Wald, R. M. (1984) General Relativity (Chicago University Press, Chicago).


Wald, R. M. (1994) Quantum Field Theory in Curved Spacetime and Black Hole Thermodynamics (Chicago University Press, Chicago).


Wambsganss, J. (1998) ‘Gravitational lensing in astronomy’, Living Rev. Relativity, 1, 12.
URL: \url{http://www.livingreviews.org/lrr-1998-12}


Ward, W. R. (1970) Astrophys. J., 162, 345.


Weber, J. (1961) General Relativity and Gravitational Waves (Interscience, New York).


Weinberg, S. (1972) Gravitation and Cosmology (Wiley, New York).


Weisberg, J. M. \& Taylor, J. H. (2005), in F. A. Rasio and I. H. Stairs (eds.), Binary Radio Pulsars (Astr. Soc. Pacific, San Francisco), pp. 25–32.


Whiting, B. F. (1989) J. Math. Phys., 30, 1301–1305.


Wiedemann, H. (2007) Particle Accelerator Physics, 3rd edn (Springer, Berlin).


Will, C. M. (1974) Astrophys. J., 191, 521.


Will, C. M. (1975) Astrophys. J., 196, 41.


Will,C.M.(1993)TheoryandExperimentinGravitationalPhysics(Cambridge University Press, 2nd edn.).


Will, C. M. (2006) ‘The confrontation between general relativity and experiment’, Living Rev. Relativity, 9, 3. URL: \url{http://www.livingreviews.org/lrr-2006-3}


Williams, L. P. (1968) Relativity Theory: Its Origins and Impact on Modern Thought (Wiley, New York).


Wilson, R. W. (1979) Rev. Mod. Phys., 51, 433.


Woodhouse, N. M. J. (2003) Special Relativity (Springer, London).


Woodhouse, N. M. J. (2007) General Relativity (Springer, London).


Woosley, S. E. \& Bloom, J. S. (2006) ‘The Supernova Gamma-Ray Burst Connection’, Ann. Rev. Astron. Astroph., 44 507–556.


Yano, K. (1955) The Theory of Lie Derivatives and its Applications (North-Holland, Amsterdam).


Yao, W.-M. et al. (2006) J. Phys. G., 33, 1. This is kept up to date on the Particle Data website, \url{http://pdg.lbl.gov/2006/reviews/contents_sports.html}

Zel’dovich, Ya. B. \& Novikov, I. D. (1971) In Thorne, K. S \& Arnett, W. D. (eds.), Stars and Relativity (Relativistic Astrophysics Vol. I) (University of Chicago Press).

}